### 2020-06-05 writeup/experiments.tex
edits

{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
The question is to predict positive or negative sentiment expressed in the text.
We use an embedding layer with GloVe embeddings
followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.

@@

{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images.
There are 14 diseases (tasks) for every image that we would like to predict.
We use AlexNet as the shared module.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.

>>>>

{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
The question is to predict positive or negative sentiment expressed in the text.
We use an embedding layer with GloVe embeddings
followed by an LSTM, MLP or CNN layer proposed by~\cite{lei2018simple}.

@@

{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images.
There are 14 diseases (tasks) for every image that we would like to predict.
We use densenet121 as the shared module.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.

### 2020-06-05 writeup/intro.tex
edits

\vspace{-0.3in}
\begin{abstract}
\vspace{-0.05in}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
	In this work, we consider three components including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} to determine transfer effect.
	We study the high-dimensional linear regression setting that allows us to define each component precisely
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	and show that the bias-variance tradeoff of multi-task estimators determines the transfer effect.
%	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Then, we explain three negative effects in multi-task learning including decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
	We validate the three effects on text classification tasks.
	Inspired by our theory, we show two practical connections of interest.
	First, single-task performance can help understand multi-task performance.
	Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.% for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

@@

Understanding positive versus negative transfer requires developing generalization bounds that scale tightly with properties of each task data such as its sample size.
This presents a technical challenge in the multi-task setting due to the presence of different task features, even for two tasks.
For Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
Without a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data is important because it is often applied to settings in which a particular task has a limited amount of samples \cite{RH19}.
%For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11}.
%On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause negative transfer \cite{YKGLHF20}.
%The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
%When all tasks are sufficiently similar, adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.

%\textbf{Setup and Main Results.}
In this work, we apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to determine transfer effect in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
To be precise, we define each component for two tasks below and our definition applies more generally.
We refer to the first task as the source and the second as the target.
\squishlist
	\item \textbf{Task similarity:} Assume that both tasks follow a linear model with parameters $\beta_1, \beta_2\in\real^p$, respectively.
	We measure the distance between them by $\norm{\beta_1 - \beta_2}$.
	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2>1$ are both fixed values that do not grow with $p$.
	We measure the source/target sample ratio by $\rho_1 / \rho_2$.
%	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
	\item \textbf{Covariate shift:} Assume that the task features are random vectors with positive semidefinite covariance matrix $\Sigma_1,\Sigma_2\in\real^{p\times p}$, respectively.
	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
	We define covariate shift as the matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
\squishend

@@

\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks.
Since the total sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than that of the single-task estimator.
Since task models are different, the bias of the multi-task estimator is \textit{always larger} than that of the single-task estimator (which is $0$ since $n_1 > p$).
Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
We provide a sharp analysis of the variance that scales only with sample size and covariate shift in Lemma \ref{lem_cov_shift_informal} and extend it to the bias.
Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
%Without loss of generality, let the $t$-th task denote the target task.
%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
%Hence adding more labeled data can help improve its test performance.
%$B\in\real^{p\times r}$
%$\set{W_i \in \real^{r}}_{i=1}^t$

@@

Second, we explain the performance of multi-task learning by varying the three components above in isotropic and covariate shifted settings.
We describe three simulations in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of the single-task estimator minus the multi-task estimator.
%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
%\textbf{Task similarity:}
%\textbf{Data sizes:}
%\textbf{Covariate shift:}
%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
\squishlist
	\item We provide a deterministic condition that depends on the sample sizes and model distance in the isotropic setting (Proposition \ref{prop_dist_transition}).
	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
	The unexplained observations are caused by an error term that arises from the bias of the multi-task estimator.
	We discuss these in Section \ref{sec_insight} more precisely.
	\item We provide a similar condition that explains a curious phenomenon in Figure \ref{fig_size}, namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
	\item We study a special case of having the same task models and show that MTL  performs best without covariate shift (Proposition \ref{prop_covariate}).
	For this special case, the bound of Lemma \ref{lem_cov_shift_informal} matches the empirical curve in Figure \ref{fig_covariate} accurately.
\squishend
%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
Along the way, we explain a key empirical finding of Taskonomy by Zamir et al. \cite{ZSSGM18}, by analyzing the benefit of MTL for reducing labeled data to achieve comparable performance to STL, .
%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.

>>>>

\vspace{-0.3in}
\begin{abstract}
\vspace{-0.05in}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	We say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
	In this work, we consider three components including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} to determine transfer effect.
	We study the high-dimensional linear regression setting that allows us to define each component precisely
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	and show that the bias-variance tradeoff of multi-task estimators determines the transfer effect.
%	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Then, we explain three negative effects in multi-task learning including decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
	We validate the three effects on text classification tasks.
	Inspired by our theory, we show two practical connections of interest.
	First, single-task performance can help understand multi-task performance.
	Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.% for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

@@

Understanding positive versus negative transfer requires developing generalization bounds that scale tightly with properties of each task data such as its sample size.
This presents a technical challenge in the multi-task setting due to the presence of different task features, even for two tasks.
For Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
Without a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data can provide guidance for downstream applications \cite{RH19}.
%For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11}.
%On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause negative transfer \cite{YKGLHF20}.
%The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
%When all tasks are sufficiently similar, adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.

%\textbf{Setup and Main Results.}
In this work, we study the bias and variance of multi-task learning in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
We apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to bound the bias and variance, and relate them to the three components.
We define each component for two tasks below and our definition applies more generally.
We refer to the first task as the source and the second as the target.
\squishlist
	\item \textbf{Task similarity:} Assume that both tasks follow a linear model with parameters $\beta_1, \beta_2\in\real^p$, respectively.
	We measure the distance between them by $\norm{\beta_1 - \beta_2}$.
	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2>1$ are both fixed values that do not grow with $p$.
	We measure the source/target sample ratio by $\rho_1 / \rho_2$.
%	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
	\item \textbf{Covariate shift:} Assume that the task features are random vectors with positive semidefinite covariance matrix $\Sigma_1,\Sigma_2\in\real^{p\times p}$, respectively.
	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
	We define covariate shift as the matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
\squishend

@@

\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks.
Since the total sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than that of the single-task estimator.
Since task models are different, the bias of the multi-task estimator is \textit{always larger} than that of the single-task estimator.
Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
We provide a sharp analysis of the variance that scales only with sample size and covariate shift in Lemma \ref{lem_cov_shift_informal} and extend it to the bias.
Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
%Without loss of generality, let the $t$-th task denote the target task.
%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
%Hence adding more labeled data can help improve its test performance.
%$B\in\real^{p\times r}$
%$\set{W_i \in \real^{r}}_{i=1}^t$

@@

Second, we explain the performance of multi-task learning by varying the three components above in isotropic and covariate shifted settings.
We describe three simulations in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of the single-task estimator minus the multi-task estimator.
%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
%\textbf{Task similarity:}
%\textbf{Data sizes:}
%\textbf{Covariate shift:}
%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
\squishlist
	\item We provide conditions to predict the effect of transfer in the isotropic setting (Proposition \ref{prop_dist_transition}).
	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
	The unexplained observations are caused by an error term from the bias.
	We discuss these in Section \ref{sec_insight}.
	\item We provide a similar condition that explains a curious phenomenon in Figure \ref{fig_size}, namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
	\item We study a special case of having the same task models and show that MTL  performs best without covariate shift (Proposition \ref{prop_covariate}).
	For this special case, the bound of Lemma \ref{lem_cov_shift_informal} matches the empirical curve in Figure \ref{fig_covariate} accurately.
\squishend
%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
Along the way, we explain a key empirical finding of Taskonomy by Zamir et al. \cite{ZSSGM18}, by analyzing the benefit of MTL for reducing labeled data to achieve comparable performance to STL.
%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.

### 2020-06-05 writeup/related.tex
edits

\textit{Multi-task learning theory.}
Some of the earliest work on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
Mauer \cite{M06} Generalization bounds for linear separation settings of MTL
Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines empirical and target errors in an optimal way.
The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
Our work is closely related to Wu et al. \cite{WZR20}.
While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques do not explain the phenomena of negative transfer.

% Adding a regularization over $B$, e.g. .
\textit{Multi-task learning methodology.}
Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
Argyriou et al. \cite{AEP08} presents a convex algorithm which learns common sparse representations across a pool of related tasks.
Evgeniou et al. \cite{EMP05} develops a framework for multi-task learning in the context of kernel methods.
%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
The multi-task learning model that we have focused on is based on the idea of hard parameter sharing \cite{C93,KD12,R17}.
We believe that the technical tools we have developed can also be applied to many other multi-task learning models.

\textit{Random matrix theory.} The random matrix theory tool and related proof of this paper fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}. For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}. It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}. On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using free addition of two independent random matrices in free probability theory \cite{nica2006lectures}. To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.

@@

In this work, we analyzed the bias and variance of multi-task learning versus single-task learning.
We provided tight concentration bounds for the bias and the variance.
Based on these bounds, we analyzed the impact of three properties, including task similarity, sample data and covariate shift on the bias and variance, to derive conditions for transfer.
%Each of these results (based on each of the 3 properties) gives a different algorithmic/practical insight.
We validated our theoretical results.
Based on the theory, we proposed to train multi-task models by incrementally adding labeled data and showed encouraging result inspired by our theory.
We describe several open questions for future work.
First, our bound on the bias term (cf. Lemma \ref{lem_cov_derivative}) involves an error term that scales down with $\rho_1$.
Tightening this error bound can potentially cover the unexplained observations in Figure \ref{fig_model_shift_phasetrans}.
Second, it would be interesting to extend our results to non-linear settings.
We remark that this likely requires addressing significant technical challenges in order to deal with non-linearity.

>>>>

\textit{Multi-task learning theory.}
Some of the earliest works on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines source and target errors in an optimal way.
The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
Our work is closely related to Wu et al. \cite{WZR20}.
While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques do not explain the phenomena of negative transfer.

% Adding a regularization over $B$, e.g. .
\textit{Multi-task learning methodology.}
Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
The multi-task learning model that we have focused on is based on the idea of hard parameter sharing \cite{C93,KD12,R17}.
We believe that the technical tools we have developed can also be applied to many other multi-task learning models.

\textit{Random matrix theory.}
The random matrix theory tool and related proof of our work fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}.
It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}. On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using the free addition of two independent random matrices in free probability theory \cite{nica2006lectures}. To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.

@@

In this work, we analyzed the bias and variance of multi-task learning versus single-task learning.
We provided tight concentration bounds for the bias and the variance.
Based on these bounds, we analyzed the impact of three properties, including task similarity, sample size, and covariate shift on the bias and variance, to derive conditions for transfer.
%Each of these results (based on each of the 3 properties) gives a different algorithmic/practical insight.
We validated our theoretical results.
Based on the theory, we proposed to train multi-task models by incrementally adding labeled data and showed encouraging results inspired by our theory.
We describe several open questions for future work.
First, our bound on the bias term (cf. Lemma \ref{lem_cov_derivative}) involves an error term that scales down with $\rho_1$.
Tightening this error bound can potentially cover the unexplained observations in Figure \ref{fig_model_shift_phasetrans}.
Second, it would be interesting to extend our results to non-linear settings.
We remark that this likely requires addressing significant technical challenges  to deal with non-linearity.

\newpage
\section*{Broader Impacts}

### 2020-06-05 writeup/setup.tex
edits

We begin by defining our problem setup including the multi-task estimator we study.
Then, we describe the bias-variance tradeoff of the multi-task estimator and connect the bias and variance of the estimator to \textit{task model distance}, \textit{sample size}, and \textit{covariate shift}.
%Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.

>>>>

We begin by defining our problem setup including the multi-task estimator we study.
Then, we describe the bias-variance tradeoff of the multi-task estimator and connect the bias and variance of the estimator to \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
%Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.
